Ants-Review: A Protocol For Open Anonymous Peer-Reviews

### 2020-06-07 paper-v1.tex
try \cite{Rinkeby} - citekeys

\newline The AntsReview Protocol is divided into stack of sub-protocols responsible for different functionality:

\begin{enumerate}
  \item \textbf{Bounty} - manage access management and the basic system.
  \item \textbf{Tokenomics} - manage system incentivization mechanism integrating ideas from DeFi and Quadratic Funding.
  \item \textbf{Privacy} - maintains the anonymity of the system via AZTEC Protocol.
\end{enumerate}

\subsubsection{Bounty}

AntsReview [\ref{appendix:b}] is the core of the smart contracts deployed on Ethereum Rinkeby's Testnet as shown in the flow-chart [Fig. \ref{fig:contracts}].
\newline It implements a Bounty-like system where an issuer (author) is asked a series of actions, to ensure transparency and robustness, regarding the AntReview that he's creating:
\begin{itemize}
  \item to upload the file containing the requirements of the peer-review and the paper into IPFS.
  \item to specify a deadline in the form of a unix timestamp after which the fulfillment will no longer be accepted.
  \item to send the amount of ether for the reward.
\end{itemize}

>>>>

\newline The AntsReview Protocol is divided into different modules responsible for the following functionalities as shown in the flow-chart [Fig. \ref{fig:contracts}]:

\begin{itemize}
\item AntsReview - manage access management and the basic system.
\item Tokenomics - manage system incentivization mechanism integrating ideas from DeFi and Quadratic Funding.
\item Privacy - maintains the anonymity of the system via AZTEC Protocol.
\end{itemize}

\subsubsection{AntsReview}

AntsReview [\ref{appendix:b}] is the core of the smart contracts deployed on Ethereum Rinkeby's Testnet \cite{Rinkeby}
\newline It implements a Bounty-like system where an issuer (author) is asked a series of actions, to ensure transparency and robustness, regarding the AntReview that he's creating:
\begin{itemize}
  \item to upload the file containing the requirements of the peer-review and the paper into IPFS.
  \item to specify a deadline in the form of a unix timestamp after which the fulfillment will no longer be accepted.
  \item to send the amount of ether for the reward.
\end{itemize}
